---
title       : Mtcars Dataset Lookup and Visualization
subtitle    : HTML slides from R Markdown
author      : Bubblesheep
job         : Statistician
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Introduction


> 1. This tool can help you get a better understanding of the "mtcars" dataset.

> 2. You can use the left side bar to choose the type of your car and a selected car list will be shown in the main window.

> 3. In the botton part of the side bar, you can choose two variables of your interest, get their mean values and check their relationship plot.

---

## Car Lookup Tool

Here you can see the variables of the 'mtcars'
```{r}
data(mtcars)
names(mtcars)
```

You can use the following popular attributes to make your own selection
```{r}
summary(mtcars[,c(1,2,4,6,9)])
```

---
## Data insight part 1

Here I provide just three simple variables to get a further insight

We have a mean function output like:
```{r}
mean(mtcars[,"mpg"])
```



---

## Data insight part 2

And we also enable the user to check the relationship plot

```{r}
plot(mpg~hp,data=mtcars)
```

Thank you for watching this!